\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles

### 2019-12-23 Response-NAR-Round1.tex

	}

	\Comment{I am also concerned by the fact that they only have one (-) No Prob condition. For both CE and MaP data, a background subtraction is required. It is not at all clear what the No Prob condition is and why it was not independently subtracted from all the data prior to analysis.}

	\Answer{There is a misunderstanding here, the “(-) No Prob” conditions refers to a baseline computational prediction that does not use any probing data as constraints (Turner energy model only). We understand that this may be confusing to the reader, and we now refer to it as “(-) No Exp” for modeling without experimental data.

	 Of course we have carried out control experiments without any modification reageant for each of the reported experiments, as now explicitly specified in the material and methods section.}

@@

	We experienced other issues while attempting to upload the raw data onto the SRA. Namely, this database requires a structured definition of the experiment, including several mandatory fields (growth culture...) that we could not reasonably fill given the nature of our experiments. In fact, a cursory search of the database showed that primary data produced by the Weeks lab is very rarely deposited in the SRA, indicating that similar difficulties are also encountered by other groups.

	We have permanently uploaded the data at:

	{\centering \url{http://www.lix.polytechnique.fr/~ponty/suppdata/ipanemap/}\\}

	and commit to its continued accessibility (but will also pursue public venues for better guarantees of a continued availability). 
	\TODO{Add minimal page and reactivities, including scripts/instructions to compute reactivities.\\ Bruno: non je pense que c'est inutile. Les reactivité sont déja données en supplémentary matérial, pour ce qui est de donner un moyen de les calculer, tout est dans l'article de weeks sur shappemapper qu'on cite. Par contre il faut déposer le script qui permet de traiter les fichier ion-torrent si ce n'est déja fait}
	}

@@

		\Answer{We also expect that additional conversion formulae, and a specific parameter calibration, for each condition, would be beneficial to the downstream predictive performances. In fact, it is one of our ongoing (recently funded) projects  to produce more extensive data for a subset of the conditions explored in this study, and to attempt to systematically learn reactivities-to-pseudo-energy conversion models.

		However, the conjunction of:
		\begin{itemize}
			\item Distinguishable, yet large-variance and highly-overlapping, reactivity distributions being observed for unpaired and paired nucleotides;
			\item High reproducibility for  reactivity profiles across repeats (and, albeit less frequently, across probes as shown in Figure A above);
		\end{itemize}
		supports the notion that the determinants of SHAPE reactivity extends far the current binary paired/unpaired model. 
		This hypothesis is already explored to some extent in \cite{Suekoesd2013}, and confirmed by recent mechanistic studies~\citep{McGinnis2012,Sexton2017,Hurst2018,Mlynsky2018,Frezza2019,Busan2019}.

		This leads us to a strong suspicion that future pseudo-energy models will have to consider more structural contexts than the current binary one. Those contexts will need to be captured by the dynamic programming schemes. The training of such extended models would probably induce a highly heterogeneous quality for pseudo-energies models trained across conditions, given  the relative scarcity of available data for certain reagents/technologies. In particular, training extended parameters would probably lead to overfitting in contexts where only a couple of reactivity profiles are currently available.

		Moreover, going back to the suggested use of the gamma distribution in the case of DMS, it is worth pointing out that \cite{Cordero2012} state in their supplementary material that
		\Quote{
		The performance of the algorithm using this probabilistic potential for SHAPE, DMS, and CMCT reactivities is given in Table S6 and is identical to
		results obtained for the standard potential with slope $m$ and intercept $b$ optimized through grid
		search .}
		We also note the relative stagnation of performances of state-of-the-art tools integrating SHAPE data, despite an increasing sophistication of the pseudo-free-energy models. So, while we believe progress can be made in the integration of reactivities, we do not expect them to radically change the quality of predicted models, nor to invalidate the findings described in this manuscript.

@@

		\Answer{
			The (hyper)parameters $m$ and $b$ were initially calibrated on the \cite{Cordero2012} dataset, revealing a very limited impact of the parameters on the prediction accuracy. We kept those values for multi probing, as the scarcity of available data did not allow us to afford an extensive cross-validation. We updated the description as shown below to be more explicit.
			\Quote{
			Those values were halved in comparison to those recommended by Deigan\etal\citep{Deigan2009}, following both a grid search optimization on the Cordero dataset, and based on the rationale that lower absolute values for pseudo-energy bonuses increase the expected overlap between pseudo-Boltzmann ensembles.}
		}

	\Comment{I am also concerned that the manuscript is not as clear as it should be about the three types of multiple data that are used.  It can use multiple reagents, probing data for multiple solution conditions, or probing data across multiple sequence variants (a.k.a. mutate and map data).  It is a real achievement that one program handles all three cases.  The abstract does state this (briefly).  The Introduction is not clear on this points, just calling the data “multiple probing data.”  Also, the text itself is sometimes unclear about what is meant.  On page 6, for example, the sentence “It is also worth mentioning that NMIA+CMCT, combining the best and worst conditions, achieves a better combined performance than DMS+NMIA, the two best mono-probing conditions.” calls these “multiple conditions”, but these data are from multiple probing reagents.  I would like to see a revised manuscript be clearer about the three types of information in the Introduction.  In the text, multiple reagents, multiple solution conditions, and multiple sequence variants should be clearly denoted as different multiple data types. }

	\Answer{
	  In the revision, we clarified several times, including at the very beginning of the Methods section, that the term "condition" encompasses a wide variety of contexts (reagent, probing technology, ionic concentrations, and sometimes even structurally-homologous mutants) leading to the production of a reactivity profile. 
	}

@@

	\Answer{
		We agree that stability of the predictions is potentially problematic, especially in the context of reproducing earlier results.

		Larger sample sizes represent a natural option for stabilizing the predictions, and indeed seem to decrease the variability. However, a substantial increase of the number $x$ of samples induces extreme computational demands, due to the current necessity to compute the dissimilarity matrix in $\Theta(x^2.n)$ time and $\Theta(x^2)$ memory. In this context, simply multiplying by 10 the number of samples would induce a 100 fold increase of the time requirement. In the future, we will revisit the clustering component to learn suitable embeddings for secondary structures, granting access to linear-time EM algorithms (eg based on Gaussian Mixture Models).

		\Quote{
	{\centering \includegraphics[width=.7\linewidth]{graphs/boxplotreproducibility}\\}
}					
		Moreover, as noted by this reviewer, an expert user would ensure a greater stability by running \OurTool several times (say 10), and electing the most recurrent structure. This process would achieve asymptotic determinism, since the frequency of a structure would converge towards real emission probabilities. Moreover, most frequent structures seem to be the best quality ones, and are emitted by \OurTool with fairly large probability, ensuring convergence in a reasonable number of iterations.
		However, such a process would be cumbersome for a basic user.

		In the future, for the sake of reproducibility, we also wish to report, and letting the user specify, a \Def{random seed}, which will  allow the exact reproduction of an analysis. However, random seeds are currently not supported by \Software{RNAsubopt}, so we are working towards their inclusion within the \Software{ViennaRNA} package.

@@

	\Comment{Third, the authors mention that Rsample was “shown to perform favorably against a comprehensive collection of state-of-the-art methods…” This is incorrect. In fact, based on a t-test, \cite{Spasic2017} concluded that “all methods that use experimental restraints perform similarly.” A similar conclusion, also based on a statistical test, was reported by \cite{Deng2016}.}

	\Answer{We thank the reviewer for pointing out this remark in the \cite{Spasic2017} paper which we overlooked in our initial reading. We corrected the corresponding sentence in our revised manuscript to
		\Quote{It was shown to perform \Rev{comparably as} a comprehensive collection of state-of-the-art methods in probing-guided structure prediction, including \Software{RME}~\citep{Wu2015}, \Software{RNAprob}~\citep{Deng2016}, \Software{RNAprobing}~\citep{Washietl2012}, \Software{RNAsc}~\citep{Zarringhalam2012} and the \Software{fold} utility from the \Software{RNAStructure} suite~\citep{Reuter2010}.}
		 This does not however challenge the conclusions drawn from this section, as \Software{RSample} remains as good a representative of the current state-of-the-art for mono-probing structure prediction.}

	\Comment{This matters because it points out a major weakness of this work, namely, it does not consider the statistical significance of its findings despite reporting substantial variability between predictions. Additionally, it highlights the possibility that a comparison to another method may result in different findings since there are a few sequences with dramatic performance gaps, which were not considered by \cite{Spasic2017}}

	\Answer{The significance (or lack thereof) of claims in the context of RNA benchmarks is, of course, a legitimate concern, and we thank the reviewer for pointing it out. The way it is used in \cite{Xu2012} should probably be taken with a grain of salt due to the dubious obedience of produced data to classic assumptions (\emph{eg} normality of distribution), but it nevertheless represents the best option available at this time.

@@

	\Answer{We already clarified that this is merely a case study. We wish we could do more (e.g. test on a wider dataset) but this is simply unrealistic, and way beyond the standards enforced for the dissemination of a new {\bf method} in structural bioinformatics.

		 However, it must be noted that we do not base our main conclusion (complementarity of probing data, benefit of their integration) solely on the \didy{} case study, but also on the Cordero dataset, where the best performances are also observed upon considering a combination of reactivity profiles associated with DMS, CMCT and NMIA probes. 
	}

	\Comment{The other reason I feel these results should be framed as a case study is that replicate data was not considered in the analysis. The manuscript attempts to differentiate between conditions or between algorithms, but the variation within each condition should be assessed in order to confirm that observed differences are in fact meaningful. }

	\Answer{We understand those reservations but, again, we need to stress that we already  {\bfseries explicitly describe this study as a case study}, and do not make any claim regarding the superiority of a given technology or probe.

	We also did reproduce in triplicate all of our SHAPE CE probing experiments (but not our SHAPE-MaP ones due to the relatively high cost and length of those experiments in our wet lab), and observed minor variations at the reactivity level, leaving us to only consider a single representative (average of available reactivities) for each experiment. We include in this revision the reactivities measured over each of the 3 replicates for each condition.
	}

### 2019-12-23 IPANEMAP-2019.tex
Updates from Overleaf

\address{%
$^{1}$\,CNRS UMR 7161, LIX, Ecole Polytechnique, 1 rue Estienne d'Orves, 91120 Palaiseau, France
and
$^{2}$\,CitCoM, Cibles th\'erapeutiques et conception de M\'edicaments, CNRS, Universit\'e de Paris, 4 avenue de l'observatoire, 75006 PARIS, France}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

@@

\noindent We introduce \OurTool{}, an automated method for the computational modeling of RNA structure from multiple probing reactivity profiles. Input profiles can result from experiments based on diverse protocols, reagents, or even a collection of mutants, and are jointly analyzed to predict the dominant conformations of an RNA.

\noindent \OurTool{} combines sampling, unsupervised learning, and multi-optimization, to produce secondary structure models that are both stable and well-supported by experimental evidences. The analysis of several reactivity, both publicly available and specifically produced experimentally, demonstrates the good performances of \OurTool, even in a mono probing setting. It confirms the potential of integrating multiple sources of probing data, leading to recommendations for the experimental design of informative probing assays.

@@

Reagents used within \Rev{selective 2 -hydroxyl acylation analyzed by primer extension (SHAPE)~\cite{Wilkinson2006} protocols} represent a popular class of small molecules. They react with the 2’-hydroxyl of flexible ribose~\cite{McGinnis2012}, although the exact properties observed by SHAPE remain the object of ongoing investigations~\cite{McGinnis2012,Sexton2017,Hurst2018,Mlynsky2018,Frezza2019,Busan2019}.
As ribose flexibility is proportional to the degree of freedom of the nucleotide, it is assumed that SHAPE reagents discriminate nucleotides in stable interactions from others. Different SHAPE reagents are endowed with different dynamics, that can help differentiate Watson-Crick base pairs from more dynamic tertiary contacts~\cite{Gherghe2008,Steen2012,Rice2014,Busan2019}. Other chemical probes, harbouring different chemical reactivities, have been developed. Amongst the most popular, DiMethyl Sulfate (DMS) is a small molecule that methylates N1 of adenines and N3 of cytosine if they are not involved in a hydrogen bond. Similarly, 1-cyclohexyl-3-(2-morpholinoethyl)carbodiimide metho-p-toluene sulfonate (CMCT) reacts on the Watson-Crick face of guanosine (N1) and uracyl (N3) when not engaged in a hydrogen bond~\cite{Ehresmann1987,Brunel2000}. These two reagents therefore mostly reveal Watson-Crick base pairing, but also any other type of contact involving the same edge. This diversity of probes not only increases coverage of the different positions and structural contexts in an RNA, but it also provides different qualitative information\Rev{, including in an \emph{in vivo} setting~\cite{Wang2019}}. It has been widely used since the very early days of RNA structure probing~\cite{Moazed1986, Ehresmann1987, Romaniuk1988, Butcher1994, Brunel2000,  Cordero2015, Somarowthu2015, Gross2017}.

@@

Computationally, the reactivity of a nucleotide is typically used as a proxy \Rev{to assess the unpaired nature of individual nucleotides}. The last couple of decades have nevertheless seen a series of paradigm shifts in the ways probing information is integrated, somehow mirroring the evolution of {\em ab initio} methods for secondary structure prediction. The seminal work of Mathews~\cite{Mathews2004} used cutoffs to transform reactivity values into hard constraints. Depending on the reagent/enzyme, significantly unreactive or reactive positions were forced to either paired or remain unpaired respectively within predicted structures. However, such \emph{hard} constraints turned out to be very sensitive to the choice of the cutoff, easily leading to artificially unpaired predictions or unsatisfiable sets of constraints. With the advent of SHAPE probing, subsequent methods lifted the requirement of thresholds and integrated reactivities directly as pseudo-energies, supplementing the Turner nearest-neighbor energy model~\cite{Turner2010} within an (pseudo) energy minimization scheme~\cite{Deigan2009,Zarringhalam2012,Washietl2012}. Such methods can be seen as optimizing a tradeoff between the thermodynamic stability of a model, assessed by the Turner energy model, and its compatibility with the reactivity profile. As a consequence, popular packages for secondary structure prediction, such as \Software{RNAStructure}~\cite{Mathews2004} or the \Software{Vienna} package~\cite{Lorenz2011}, now routinely accept SHAPE-like reactivity profiles as input of their main structure prediction methods. \Rev{Besides free-energy optimization, such methods notably} include the joint folding of aligned RNAs~\cite{Lavender2015}, partition function, statistical sampling and Maximal Expected Accuracy predictions~\cite{Spasic2017}\ldots

@@

\subsection*{The \OurTool{} method}
We introduce the Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles (\OurTool{}), a novel approach that integrates the signals produced by various chemical probes \Rev{to predict one or several secondary structure models for a given RNA.}

It performs a structural clustering across multiple sets of structures sampled in different experimental conditions, and ultimately returns a set of structures that are representative of the dominant conformations supported across conditions. Its underlying rationale is that the prominent presence of a stable secondary structure within the  (pseudo-)Boltzmann ensembles induced by multiple experimental conditions should increase its likelihood to be (one of) the native structure(s) for a given RNA. It is thus hoped that integrating several reactivity profiles may be used to promote the native structure as one of the dominant structures within the multi-ensemble, and help circumvent the limitation of pseudo-energies derived from single reactivity profile, which are generally not sufficient to elect the native structure as its minimum (pseudo)-free energy candidate. In other words, combining ensembles of structures generated using multiple probing experiments is likely to denoise the Boltzmann (multi-)ensemble, and thus mitigate systematic biases induced by experimental conditions and reagents.

@@

\didy{} was probed with different SHAPE reagents: 1M7 (1-methyl-7 nitrosatoic anhydre), NMIA (N-Methyl Isatoic Anhydre), BzCN (Benzoyl cyanide) and NAI (2-methylnicotinic acid imidazolide) in presence and absence of Mg$^\text{2+}$. \Rev{\didy{} was also probed with DMS (DiMethylSulfate) and CMCT, this time only in presence of Mg$^\text{2+}$, resulting in a total of 16 \Def{probing conditions}, a term we use in the following to denote a combination of probing technology, reagent and presence/absence of Mg$^\text{2+}$ (+ sequencing technology). For each probing condition, three experiments were performed in presence/absence of the reagent, and in a denatured context, following classic SHAPE protocols~\cite{Wilkinson2006,Smola2015}.}

@@

	\caption{Dot-bracket representations of the native structure and \OurTool{} predictions for the glycine riboswitch sequence of the Cordero\etal\cite{Cordero2012} data set, supplemented with an increasing collection of probing conditions. Positions with green and red backgrounds indicate correctly and incorrectly predicted base pairs.}\label{fig:glycine_example}

@@

This trend is confirmed when two random mutants were considered in addition to the WT (WT+2M), with an average MCC across runs increasing to 66.6\%. %mean(Multiprobing_2M).
Interestingly, the dispersion of the MCC was lower for WT+2M than for WT+1M, with lower MCC values above 57\%.  This results suggest  a role of \emph{tie-breaker} for the third condition, allowing to mitigate the deleterious effect of some outlier.
However, outliers still played a disruptive role, and restricting chosen mutants to the 20 reactivity profiles most similar to the WT further improved the average MCC 2.8\% to 67.7\%,  \Rev{ a significant improvement compared to WT+1M (P-value$=2.4\times10^{-2}$).}

>>>>

\address{%
$^{1}$\,CNRS UMR 7161, LIX, Ecole Polytechnique, 1 rue Estienne d'Orves, 91120 Palaiseau, France
and
$^{2}$\,CNRS UMR 8038, CitCoM, Universit\'e de Paris, 4 avenue de l'observatoire, 75006 Paris, France}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

@@

\noindent We introduce \OurTool{}, an automated method for the modeling of RNA structure from multiple probing reactivity profiles. Input profiles can result from experiments based on diverse protocols, reagents, \Rev{or collection of variants}, and are jointly analyzed to predict the dominant conformations of an RNA.

\noindent \OurTool{} combines sampling, \Rev{clustering}, and multi-optimization, to produce secondary structure models that are both stable and well-supported by experimental evidences. The analysis of multiple reactivity profiles, both publicly available and produced in our study, demonstrates the good performances of \OurTool, even in a mono probing setting. It confirms the potential of integrating multiple sources of probing data, informing the design of informative probing assays.

@@

Reagents used within \Rev{selective 2' -hydroxyl acylation analyzed by primer extension (SHAPE)~\cite{Wilkinson2006} protocols} represent a popular class of probes. They react with the 2’-hydroxyl of flexible ribose~\cite{McGinnis2012}, although the exact properties observed by SHAPE remain the object of ongoing investigations~\cite{McGinnis2012,Sexton2017,Hurst2018,Mlynsky2018,Frezza2019,Busan2019}.
As ribose flexibility is proportional to the degree of freedom of the nucleotide, it is assumed that SHAPE reagents discriminate nucleotides involved in stable interactions. Different SHAPE reagents are endowed with different dynamics, that can help differentiate Watson-Crick base pairs from more dynamic tertiary contacts~\cite{Gherghe2008,Steen2012,Rice2014,Busan2019}. Other chemical probes, harbouring different chemical reactivities, have been developed. Amongst the most popular, DiMethyl Sulfate (DMS) is a small molecule that methylates Adenines and Cytosines if not involved in a hydrogen bond, while   CMCT reacts with the Watson-Crick face of unpaired Guanosines and Uracyls~\cite{Ehresmann1987,Brunel2000}. These two reagents not only reveal Watson-Crick base pairing, but also other types of contacts involving the same edge. The diversity of probes\Rev{, some of which are usable \emph{in vivo},} not only increases coverage of the different positions and structural contexts, \Rev{but also provides different qualitative information. \Rev{Modeling can also benefit from a joint analysis of reactivity profiles of single-point mutants, assuming structural homology~\cite{Cordero2012a}}. Integration of multiple sources of probing to improve structure prediction  has thus been widely used since the very early days of RNA structure probing~\cite{Moazed1986, Ehresmann1987, Romaniuk1988, Butcher1994, Brunel2000,  Cordero2015, Somarowthu2015, Gross2017} but, to the best of our knowledge, has never been fully automated.}

@@

Computationally, the reactivity of a nucleotide is typically used as a proxy \Rev{to assess the unpaired nature of individual nucleotides}. The past couple of decades have nevertheless seen a series of paradigm shifts in the ways probing information is integrated, somehow mirroring the evolution of {\em ab initio} methods for secondary structure prediction. The seminal work of Mathews~\cite{Mathews2004} used cutoffs to transform reactivity values into hard constraints. Depending on the used reagent/enzyme, significantly unreactive or reactive positions were forced to remain paired or  unpaired within predicted models. However, such \emph{hard constraints} can be overly  sensitive to the choice of the cutoff, leading to artificially unpaired predictions or unsatisfiable sets of constraints. With the advent of SHAPE probing~\cite{Smola2015}, new methods~\cite{Deigan2009,Zarringhalam2012,Washietl2012} lifted the requirement of a threshold, supplementing  Turner nearest-neighbor energy model~\cite{Turner2010} with pseudo-energies derived from the reactivities. They  then performed a (pseudo) energy minimization, optimizing a tradeoff between the thermodynamic stability and its compatibility with the reactivity profile. Popular packages for secondary structure prediction, such as \Software{RNAStructure}~\cite{Mathews2004} or the \Software{Vienna} package~\cite{Lorenz2011}, now routinely accept SHAPE-like reactivity profiles as input of their main structure prediction methods. \Rev{Besides free-energy optimization, such methods notably} include the joint folding of aligned RNAs~\cite{Lavender2015}, partition function, statistical sampling and Maximal Expected Accuracy predictions~\cite{Spasic2017}\ldots

@@

\subsection*{The \OurTool{} method}
We introduce the Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles (\OurTool{}), a novel approach that integrates the signals produced by various \Rev{probing experiments to predict one or several secondary structure models for a given RNA. It takes as input one or several reactivity profiles produced in various \Def{conditions}, broadly defined to denote the conjunction of a reagent, a probing technology, ionic concentrations and, in extreme cases, structurally homologous mutants.}

It performs a structural clustering across multiple sets of structures sampled in different experimental conditions, and ultimately returns a set of structures representing dominant conformations supported across conditions. Its underlying rationale is that the prominent presence of a stable secondary structure within the  (pseudo-)Boltzmann ensembles induced by multiple experimental conditions should increase its likelihood to be (one of) the native structure(s) for a given RNA. It is thus hoped that integrating several reactivity profiles may be used to promote the native structure as one of the dominant structures within the multi-ensemble, and help circumvent the limitation of pseudo-energies derived from single reactivity profile, which are generally not sufficient to elect the native structure as its minimum (pseudo)-free energy candidate. In other words, combining ensembles of structures generated using multiple probing experiments is likely to denoise the Boltzmann (multi-)ensemble, and thus mitigate systematic biases induced by experimental conditions and reagents.

@@

\didy{} was probed with different SHAPE reagents: 1M7 (1-methyl-7 nitrosatoic anhydre), NMIA (N-Methyl Isatoic Anhydre), BzCN (Benzoyl cyanide) and NAI (2-methylnicotinic acid imidazolide) in presence and absence of Mg$^\text{2+}$. \Rev{\didy{} was also probed with DMS (DiMethylSulfate) and CMCT, in presence of Mg$^\text{2+}$, resulting in a total of 16 \Def{probing conditions}, a term we use in the following to denote a combination of probing technology, reagent and presence/absence of Mg$^\text{2+}$ (+ sequencing technology). For each probing condition, three experiments were performed in presence/absence of the reagent, and in a denatured context, following classic SHAPE protocols~\cite{Wilkinson2006,Smola2015}.}

@@

	\caption{Dot-bracket representations of the native structure and \OurTool{} predictions for the glycine riboswitch sequence of the Cordero\etal\cite{Cordero2012} data set, supplemented with an increasing collection of probing conditions. \Rev{Please note that, throughout the manuscript, by "conditions" we mean a combination of the nature of the probe, the probing technology, the ions present, the temperature, or any other "environmental" variation} Positions with green and red backgrounds indicate correctly and incorrectly predicted base pairs.}\label{fig:glycine_example}

@@

This trend is confirmed when two random mutants were considered in addition to the WT (WT+2M), with an average MCC across runs increasing to 66.6\%. %mean(Multiprobing_2M).
Interestingly, the dispersion of the MCC was lower for WT+2M than for WT+1M, with lower MCC values above 57\%.  This results suggest \Rev{adding a second mutant profile has  a role of \emph{tie-breaker}}, allowing to mitigate the deleterious effect of some outlier.
However, outliers still played a disruptive role, and restricting chosen mutants to the 20 reactivity profiles most similar to the WT further improved the average MCC 2.8\% to 67.7\%,  \Rev{ a significant improvement compared to WT+1M (P-value$=2.4\times10^{-2}$).}
